%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Yanjie Song} % Your name
\address{(+86) 189-5200-9027} % Your secondary addess (optional)
\address{songyj@shanghaitech.edu.cn \\ www.icarusradio.top} % Your phone number and email
\address{393 Middle Huaxia Road, Pudong, Shanghai, China 201210} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf ShanghaiTech University} \hfill {Shanghai, China} 
\\ B.E. in Computer Science and Technology \hfill {Sep. 2016 - Jul. 2020}
\begin{itemize}
    \item GPA: 3.45/4.0
    \item Core courses:
\end{itemize}
\begin{center}
\begin{tabular}{llll}
Programming & & Data Structures &\\
Computer Architecture I & & Computer Architecture II & (graduate)\\
Operating Systems & & Computer Networks & \\
\end{tabular}
\end{center}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Project}
{\bf ShanghaiTech SC Team} \hfill {Shanghai, China}\\
\textit{Member} \hfill {Feb. 2019 - Nov. 2019}
\begin{itemize}
    \item Participate in the design of a high-performance computing (HPC) system and take part in the HPC competition.
\end{itemize}

{\bf Berkeley CS61C Course Project} \hfill {Mar. 2018 - Jun. 2018}
\begin{itemize}
    \item Learn Berkeley CS61C (2017 Summer) course by myself
    \item Finish the course project by myself
\end{itemize}

{\bf Stanford CS140 Course Project} \hfill {Mar. 2018 - Jun. 2018}
\begin{itemize}
    \item Learn Stanford CS140 (2018 Winter) course by myself
    \item Finish the course project by myself
\end{itemize}
\end{rSection}

\begin{rSection}{Teaching experience}
CS 130 Operating Systems I, ShanghaiTech University \hfill {Shanghai, China}\\
\textit{Teaching Assistant} \hfill {Sep. 2018 - Jan. 2019}
\begin{itemize}
    \item Led discussion session on C/Operating Systems and held office hour for 110 sophomores.
    \item Designed one assignment.
\end{itemize}

CS 110 Computer Architecture I, ShanghaiTech University \hfill {Shanghai, China}\\
\textit{Teaching Assistant} \hfill {Feb. 2019 - Jun. 2019}
\begin{itemize}
    \item Led discussion session on C/RISC-V/Parallel Computing and held office hour for 110 sophomores.
    \item Designed two assignments and created problems for three exams.
\end{itemize}
\end{rSection}

\begin{rSection}{Skills}
{\bf Programming languages:} C/C++, Python, Rust\\
{\bf Tools:} CMake, Git, \LaTeX, Nginx\\
{\bf Hardware:} Raspberry Pi, Pine64
\end{rSection}
\end{document}
